Plots

### 2025-02-27 src/plots.Rmd
Finish most plots

@@

    # Calc csmf acc
    out <- 1 - (sum(abs(csmf_true - csmf_pred)) / csmf_max_error)
    return(out)
}
```

@@

# Plot performance of models
plot_perf <- function(
        df_long,
        f = calc_pccc,
        group = "cod_name",
        title = NULL,
        x_title = NULL,
        y_title = NULL,
        text_mid_size = 2,
        text_mid_vjust = 2.5,
        text_end_size = 3,
        text_hjust = 0.2,
        add_min_points = F,
        add_max_points = F,
        mid_points_size = 1.5,
        min_points_size = 2,
        max_points_size,
        x_limits = c(0, 1),
        ...
    ) {

    # Calc metric
    df_plot <- df_long %>%
        group_by(.data[[group]], model_name, .drop = F) %>%
        summarize( # calc pccc
            metric = f(cod, model_cghr10, N = unique(ncod)[1], ...)
        ) %>%
        mutate( # add pccc to model name
            model_label = paste0(model_name, " (", round(metric, 2), ")")
        )

    # Add min and max values for each cause of death
    df_ends <- df_plot %>%
        group_by(.data[[group]]) %>%
        summarize(
            min_metric = min(metric),
            max_metric = max(metric),
            model_min = model_name[which.min(metric)],
            model_max = model_name[which.max(metric)]
        ) %>%
        arrange(max_metric)

    # Sort cod by max model metric
    df_plot[[group]] <- factor(df_plot[[group]], levels = df_ends[[group]])
    df_ends[[group]] <- factor(df_ends[[group]], levels = df_ends[[group]])

@@

    # Plot metric for each model
    out <- ggplot(df_plot, aes(x = metric, y = .data[[group]])) +
        geom_point( # mid points
            data = df_mids,
            size = mid_points_size
        ) +
        geom_segment( # min max lines
            data = df_ends,
            aes(
                x = min_metric,
                xend = max_metric,
                y = .data[[group]],
                yend = .data[[group]]
            ),
            linewidth = 0.75
        ) +
        geom_text( # min model text
            data = df_ends,
            aes(
                x = min_metric,
                y = .data[[group]],
                label = paste0(model_min, " (", round(min_metric, 2), ")")
            ),
            hjust = 1 + text_hjust,
            vjust = 0.5,
            size = text_end_size
        ) +
        geom_text( # max model text
            data = df_ends,
            aes(
                x = max_metric,
                y = .data[[group]],
                label = paste0(model_max, " (", round(max_metric, 2), ")")
            ),
            hjust = 0 - text_hjust,
            vjust = 0.5,
            size = text_end_size
        ) +
        geom_text_repel( # mid model text
            data = df_mids,
            aes(label = model_label),
            color = "gray60",
            vjust = text_mid_vjust,
            max.overlaps = Inf,
            size = text_mid_size
        ) +
        scale_x_continuous(
            limits = x_limits,
            expand = expansion(add = 0.2)
        ) +
        labs(
            title = title,
            x = x_title,
            y = y_title
        ) +
        theme_minimal() +
        theme(
            panel.border = element_rect(
                color = "black",
                fill = NA,
                linewidth = 0.5
            ),
            legend.position = "none",
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank()
        )

@@

@@

# Shorten COD names
df <- df %>%
    mutate(physician_cghr10 = str_wrap(physician_cghr10, width = 34))

@@

@@

# Number of causes for each age group
ncod_adult <- 19
ncod_child <- 10
ncod_neo <- 7

@@

# Pivot data into long format for calc
df_long <- df %>%
    filter( # remove low count cod
        physician_cghr10_n >= 10
    ) %>%
    pivot_longer( # long format
        ends_with("_cghr10") & !starts_with("physician_"),
        names_to = "model",
        values_to = "model_cghr10"
    ) %>%
    mutate(
        model = str_replace( # remove cghr10
            model,
            "_cghr10",
            ""
        ),
        model_name = str_replace_all(model, "_", " or ") %>% # use full model names
            str_replace(., "gpt3", gpt3_name) %>%
            str_replace(., "gpt4", gpt4_name) %>%
            str_replace(., "insilicova", isva_name) %>%
            str_replace(., "interva5", iva5_name),
        age_name = case_when( # use full age name
            age == "adult" ~ "Adult",
            age == "child" ~ "Child",
            age == "neo" ~ "Neonate",
            .default = NA
        ),
        cod = physician_cghr10,
        cod_name = paste0(
            cod,
            "\n(n=", physician_cghr10_n, ", ", round(physician_cghr10_perc), "%)"
        ),
        ncod = case_when( # num of cods for each age group
            age == "adult" ~ ncod_adult,
            age == "child" ~ ncod_child,
            age == "neo" ~ ncod_neo,
            .default = NA
        )
    ) %>%
    filter( # remove combine models
        !str_detect(model_name, " or ")
    )

@@

@@

```{r}
plot_perf(
    df_long %>%
        mutate(
            age_label = case_when(
                age_name == "Adult"
                    ~ paste0(age_name, "\n12+ Years\n(n=", n_adult, ", ", round(perc_adult), "%)"),
                age_name == "Child"
                    ~ paste0(age_name, "\n28 Days to 11 Years\n(n=", n_child, ", ", round(perc_child), "%)"),
                age_name == "Neonate"
                    ~ paste0(age_name, "\n<28 Days\n(n=", n_neo, ", ", round(perc_neo), "%)"),
                .default = age_name
            )
        ),
    calc_pccc,
    group = "age_label",
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    y_title = paste0("Physician Agreed Records (n=", nrow(df), ")"),
    text_mid_size = 2.5,
    text_mid_vjust = 3
)
```

## PCCC by COD

Age, stage, cod.

@@

# Plot perf for pccc
plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    group = "cod_name",
    title = paste0("(a) Adult, 12+ Years (n=", n_adult, ")"),
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    y_title = "Cause of Death"
) /
    plot_perf(
        df_long %>% filter(age == "child"),
        calc_pccc,
        group = "cod_name",
        title = paste0("(b) Child, 28 Days to 11 Years (n=", n_child, ")"),
        x_title = "Partial Chance Corrected Concordance (PCCC)",
        y_title = "Cause of Death"
    ) /
    plot_perf(
        df_long %>% filter(age == "neo"),
        calc_pccc,
        group = "cod_name",
        title = paste0("(c) Neonatal, <28 Days (n=", n_child, ")"),
        x_title = "Partial Chance Corrected Concordance (PCCC)",
        y_title = "Cause of Death",
        text_mid_vjust = 3
    ) +
    plot_layout(
        heights = c(2, 1, 1),
        axis_titles = "collect"
    )

@@

## CSMF Accuracy

Calculate Cause Specific Mortality Fraction (CSMF) Accuracy to evaluate population performance for each model by age and physician coding stage.

@@

# Create csmf for each age group
csmf_adult <- list()
csmf_child <- list()
csmf_neo <- list()

@@

## Plots

Save calculated metrics to `data` folder.

```{r}
out <- reduce(metrics,
              function(x, y) left_join(x, y, by = "Model")
)
write_csv(out, "../data/healsl_rd1to2_metrics_v1.csv")
```

### Exploration

@@

# Num and perc of agreed cases
nall <- nrow(df)
nagree <- nrow(df %>% filter(is_agreed == TRUE))
pagree <- (nagree / nall) * 100

# Create labels to axis titles
y_title <- paste0("Physician Agreed Records (n=", nagree, ", 100%)")
```

#### Cases by Sex and Age Group

Display a plot of cases by age group separated by sex.

@@

# Calc age and sex counts
nadult <- nrow(df %>% filter(age == "adult" & is_agreed == TRUE))
nchild <- nrow(df %>% filter(age == "child" & is_agreed == TRUE))
nneo <- nrow(df %>% filter(age == "neo" & is_agreed == TRUE))

# Calc age and sex perc
padult <- (nadult / nagree) * 100
pchild <- (nchild / nagree) * 100
pneo <- (nneo / nagree) * 100

# Create age with counts
age_remap <- c(
    "Adult" = paste0("Adult, 12+ years\n(n=", nadult, ", ", round(padult), "%)"),
    "Child" = paste0("Child, 28 days to 11 years\n(n=", nchild, ", ", round(pchild), "%)"),
    "Neo" = paste0("Neonatal, <28 days\n(n=", nneo, ", ", round(pneo), "%)")
)

# Format the data for plotting
asdata <- df %>%
    filter(is_agreed == TRUE) %>%
    group_by(age, sex) %>%
    summarize(count = n()) %>%
    mutate(
        age = str_to_title(age),
        sex = paste0(
            sex, " (n=", count, ", ",
            round(count / case_when(
                age == "Adult" ~ nadult,
                age == "Child" ~ nchild,
                age == "Neo" ~ nneo
            ) * 100), "%)"
        )
    ) %>%
    mutate( # re-order age
        age = factor(age, levels = c(
            "Adult",
            "Child",
            "Neo"
        ))
    ) %>%
    mutate( # rename ages with counts
        age = recode(age, !!!age_remap)
    )

# Plot the data
asplot <- asdata %>%
    ggplot(aes(x = factor(age), y = count, fill = sex)) +
    geom_bar(
        stat = "identity",
        fill = "white",
        color = "black"
    ) +
    geom_text(
        aes(label = sex),
        position = position_stack(vjust = 0.5),
        size = 2.5,
        color = "black"
    ) +
    labs(
        y = y_title,
        x = element_blank(),
        fill = "Sex"
    ) +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.title.y = element_text(margin = margin(r = 10))
    )

# Save the plot
asplot
ggsave("../manuscript/fig-data-agesex.pdf", plot = asplot, dpi = 300)
```

#### Cases by Age Range

Display a plot for each age group of cases by age range.

```{r}
for (a in c("adult", "child", "neo")) {

    # Create label for age group
    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
    atitle <- paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")

    # Format plot data
    eardata <- df %>%
        filter(is_agreed == TRUE & age == a) %>%
        group_by(age_range) %>%
        summarize(count = n()) %>%
        separate(
            age_range,
            into = c("age_range_value", "age_range_unit"),
            sep = " "
        ) %>%
        separate(
            age_range_value,
            into = c("age_range_min", "age_range_max"),
            sep = "-"
        ) %>%
        mutate(
            age_range_min = as.integer(age_range_min),
            age_range_max = as.integer(age_range_max),
            age_range_unit = factor(age_range_unit, levels = c(
                "Weeks",
                "Days",
                "Months",
                "Years"
            )),
            age_range_label = paste0(
                age_range_min,
                "-",
                age_range_max,
                " ",
                age_range_unit,
                "\n(n=", count, ", ", round((count / arows) * 100), "%)"
            )
        ) %>%
        arrange(age_range_unit, age_range_min, age_range_max) %>%
        mutate(
            age_range_label = factor(age_range_label, levels = unique(age_range_label))
        )

    # Plot the data
    earplot <- eardata %>%
        ggplot(aes(x = age_range_label, y = count)) +
        geom_bar(
            stat = "identity",
            fill = "#1d1d1d",
            color = "white",
            width = 0.5
        ) +
        labs(
            y = atitle,
            x = element_blank()
        ) +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10))
        ) +
        coord_flip()

    # Save the plot
    print(earplot)
    ggsave(
        sprintf("../manuscript/fig-data-agerange-%s.pdf", a),
        plot = earplot,
        dpi = 300
    )
}
```

#### Cases by COD

Display a plot for each age group of cases by cause of death.

```{r}
for (a in c("adult", "child", "neo")) {

    # Create label for age group
    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
    atitle <- paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")

    # Format plot data
    ecoddata <- df %>%
        filter(is_agreed == TRUE & age == a) %>%
        group_by(physician_cghr10) %>%
        summarize(count = n()) %>%
        mutate(
            cod_label = paste0(
                if_else(
                    str_count(physician_cghr10, "\\s+") > 3,
                    str_replace(physician_cghr10, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n"),
                    physician_cghr10
                ),
                "\n(n=", count, ", ",
                if_else(
                    ((count / arows) * 100) < 1,
                    "<1",
                    as.character(round((count / arows) * 100))
                ), "%)"
            )
        ) %>%
        arrange(count) %>%
        mutate(
            cod_label = factor(cod_label, levels = unique(cod_label))
        )

    # Plot the data
    ecodplot <- ecoddata %>%
        ggplot(aes(x = cod_label, y = count)) +
        geom_bar(
            stat = "identity",
            fill = "#1d1d1d",
            color = "white",
            width = 0.5
        ) +
        labs(
            y = atitle,
            x = element_blank()
        ) +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10)),
            axis.text.x = element_text(hjust = 1)
        ) +
        coord_flip()

    # Save the plot
    print(ecodplot)
    ggsave(
        sprintf("../manuscript/fig-data-cod-%s.pdf", a),
        plot = ecodplot,
        dpi = 300,
        width = if (a == "adult") 6 else NA,
        height = if (a == "adult") 8 else NA
    )
}
```

### Performance

#### All vs Agree Performance

Display a plot of model performance for all records versus records where physicians agreed on the COD code.

```{r, fig.height = 2.5, fig.width = 6}

# Calc stage counts
nall <- nrow(df)
nagree <- nrow(df %>% filter(is_agreed == TRUE))
nrecon <- nrow(df %>% filter(is_recon == TRUE))
nadj <- nrow(df %>% filter(is_adj == TRUE))

# Calc stage perc
pagree <- (nagree / nall) * 100
precon <- (nrecon / nall) * 100
padj <- (nadj / nall) * 100

# Create stage with counts
stage_remap <- c(
    "All" = paste0("All\nRecords\n(n=", nall, ", 100%)"),
    "Agreed" = paste0("Physician Agreed\nRecords\n(n=", nagree, ", ", round(pagree), "%)"),
    "Reconciled" = paste0("Reconciled\n(n=", nrecon, ", ", round(precon), "%)"),
    "Adjudicated" = paste0("Adjudicated\n(n=", nadj, ", ", round(padj), "%)")
)

# Prepare boxplot data
alldata <- out %>%
    select(
        Model,
        `PCCC`,
        `PCCC Agreement`,
        `CSMF Accuracy`,
        `CSMF Accuracy Agreement`
    ) %>%
    rename(
         All = `PCCC`,
         Agreed = `PCCC Agreement`
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -c(
            Model,
            `CSMF Accuracy`,
            `CSMF Accuracy Agreement`
        ),
        names_to = "Stage",
        values_to = "PCCC"
    ) %>%
    group_by(Stage) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) + 0.05,
            paste0(
                Model, "\n(",
                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
                "CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) - 0.05,
            paste0(
                Model, "\n(",
                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
                "CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(Model, "\n(", round(PCCC, 2), ", CSMF=", round(if_else(Stage == "All", `CSMF Accuracy`, `CSMF Accuracy Agreement`), 2), ")"),
            NA
        ),
        "PCCC Mid Value" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            PCCC,
            NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        )
    ) %>%
    mutate( # re-order stage
        Stage = factor(Stage, levels = c(
            "Agreed",
            "All"
        ))
    ) %>%
    mutate( # rename stages with counts
        Stage = recode(Stage, !!!stage_remap)
    )

>>>>

## Data Functions

# Order textual age ranges
order_arange <- function(ages) {
    out <- ages %>%
        data.frame %>%
        rename("age_range" = ".") %>%
        separate( # sep into range and unit
            age_range,
            into = c("age_range", "unit"),
            sep = " "
        ) %>%
        separate( # sep into min and max age
            age_range,
            into = c("age_min", "age_max"),
            sep = "-"
        ) %>%
        mutate( # format into correct data types
            age_min = as.integer(age_min),
            age_max = as.integer(age_max),
            unit = str_to_lower(unit) %>%
                factor(., levels = c(
                    "hours",
                    "days",
                    "weeks",
                    "months",
                    "years"
                ))
        ) %>%
        arrange(unit, age_min, age_max) %>% # sort ages
        mutate( # create ordered ages
            age_range = paste0(age_min, "-", age_max, " ", unit)
        ) %>%
        pull(age_range)
    return(out)
}

@@

    # Calc csmf acc
    out <- 1 - (sum(abs(csmf_true - csmf_pred)) / csmf_max_error)
    return(out)
}

@@

# Plot performance of models using lines and points
plot_perf <- function(
        df_long,
        f = calc_pccc,
        group = "cod_name",
        text_scale = 1,
        title = NULL,
        title_size = 10,
        x_title = NULL,
        y_title = NULL,
        text_mid_size = 2 * text_scale,
        text_mid_vjust = 2.5,
        text_end_size = 3 * text_scale,
        text_hjust = 0.1,
        add_min_points = F,
        add_max_points = F,
        mid_points_size = 1.5,
        min_points_size = 2,
        max_points_size,
        x_limits = c(0, 1),
        x_breaks = seq(0, 1, by = 0.1),
        x_expand = expansion(add = 0.2),
        x_title_size = 9 * text_scale,
        y_title_size = 9 * text_scale,
        x_text_size = 8 * text_scale,
        y_text_size = 9 * text_scale,
        sort_group = T,
        ...
    ) {

    #  Group data
    df_plot <- df_long %>%
        group_by(.data[[group]], model_name, .drop = F)

    # Calc metric
    if (identical(f, calc_pccc)) {
        df_plot <- df_plot %>%
            summarize(
                metric = f(cod, model_cghr10, N = unique(ncod)[1], ...)
            )
    } else {
        df_plot <- df_plot %>%
            summarize(
                metric = f(cod, model_cghr10, ...)
            )
    }

    # Add metric value to model name
    df_plot <- df_plot %>%
        mutate( 
            model_label = paste0(model_name, " (", round(metric, 2), ")")
        )

    # Add min and max values for each group
    df_ends <- df_plot %>%
        group_by(.data[[group]]) %>%
        summarize(
            min_metric = min(metric),
            max_metric = max(metric),
            model_min = model_name[which.min(metric)],
            model_max = model_name[which.max(metric)]
        ) %>%
        arrange(max_metric)

    # Sort group by max model metric
    if (sort_group) {
        df_plot[[group]] <- factor(df_plot[[group]], levels = df_ends[[group]])
        df_ends[[group]] <- factor(df_ends[[group]], levels = df_ends[[group]])
    }

@@

    # Plot metric for each model
    out <- ggplot(df_plot, aes(x = metric, y = .data[[group]])) +
        geom_point( # mid points
            data = df_mids,
            size = mid_points_size
        ) +
        geom_segment( # min max lines
            data = df_ends,
            aes(
                x = min_metric,
                xend = max_metric,
                y = .data[[group]],
                yend = .data[[group]]
            ),
            linewidth = 0.75
        ) +
        geom_text( # min model text
            data = df_ends,
            aes(
                x = min_metric,
                y = .data[[group]],
                label = paste0(model_min, " (", round(min_metric, 2), ")")
            ),
            hjust = 1 + text_hjust,
            vjust = 0.5,
            size = text_end_size
        ) +
        geom_text( # max model text
            data = df_ends,
            aes(
                x = max_metric,
                y = .data[[group]],
                label = paste0(model_max, " (", round(max_metric, 2), ")")
            ),
            hjust = 0 - text_hjust,
            vjust = 0.5,
            size = text_end_size
        ) +
        geom_text_repel( # mid model text
            data = df_mids,
            aes(label = model_label),
            color = "gray60",
            vjust = text_mid_vjust,
            max.overlaps = Inf,
            size = text_mid_size
        ) +
        scale_x_continuous(
            limits = x_limits,
            breaks = x_breaks,
            expand = x_expand
        ) +
        labs(
            title = title,
            x = x_title,
            y = y_title
        ) +
        theme_minimal() +
        theme(
            panel.border = element_rect(
                color = "black",
                fill = NA,
                linewidth = 0.75
            ),
            legend.position = "none",
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            plot.title = element_text(size = title_size),
            axis.title.x = element_text(size = x_title_size),
            axis.title.y = element_text(size = y_title_size),
            axis.text.x = element_text(size = x_text_size),
            axis.text.y = element_text(size = y_text_size)
        )

@@

# Plot perf of models using trend lines
plot_perf_trend <- function(
        df_long,
        f = calc_pccc,
        group = "age_range",
        text_scale = 1,
        title = NULL,
        x_title = NULL,
        y_title = NULL,
        title_size = 10,
        x_title_size = 9 * text_scale,
        y_title_size = 9 * text_scale,
        x_text_size = 8 * text_scale,
        y_text_size = 9 * text_scale,
        legend_text_size = 9 * text_scale,
        legend_position = "bottom",
        legend_direction = "horizontal",
        legend_spacing = unit(0, "pt")
    ) {

    # Calc metric
    df_plot <- df_long %>%
        group_by(.data[[group]], model_name, .drop = F) %>%
        summarize( # calc pccc
            age = paste0(unique(age), collapse = ","),
            metric = f(cod, model_cghr10, N = unique(ncod)[1])
        ) %>%
        mutate( # add pccc to model name
            model_label = paste0(model_name, " (", round(metric, 2), ")")
        )

    # Get custom colors for models
    default_colors <- scales::hue_pal()(length(unique(df_plot$model_name)))
    names(default_colors) <- unique(df_plot$model_name)
    default_colors["Mean"] <- "black"

    # Plot trend lines for each model
    out <- ggplot(
        df_plot,
        aes(
            x = .data[[group]],
            y = metric,
            color = model_name,
            group = model_name
        )
    ) +
        geom_line(linewidth = 0.75, alpha = 0.4) + 
        geom_line(
            data = df_plot %>%
                group_by(.data[[group]]) %>%
                summarize(
                    metric = mean(metric),
                    model_name = "Mean"
                ),
            aes(color = model_name),
            se = F,
            linewidth = 1.25
        ) +
        scale_color_manual(values = default_colors) +
        labs(
            title = title,
            x = x_title,
            y = y_title
        ) +
        theme_minimal() +
        theme(
            panel.border = element_rect(
                color = "black",
                fill = NA,
                linewidth = 0.75
            ),
            legend.title = element_blank(),
            legend.text = element_text(size = legend_text_size),
            legend.position = legend_position, 
            legend.direction = legend_direction,
            legend.box.spacing = legend_spacing,
            plot.title = element_text(size = title_size),
            axis.title.x = element_text(size = x_title_size),
            axis.title.y = element_text(size = y_title_size),
            axis.text.x = element_text(size = x_text_size),
            axis.text.y = element_text(size = y_text_size)
        )
    return(out)

}

@@

# Shorten COD names
df <- df %>%
    mutate(across(
        c(
            physician_cghr10,
            gpt3_cghr10,
            gpt4_cghr10,
            insilicova_cghr10,
            interva5_cghr10
        ),
        ~ str_wrap(.x, width = 18)
    ))

## Standardize Age Ranges

Standardize age ranges to follow age range and unit format in lowercase.

# Standardize ages to age range + unit
df <- df %>%
    mutate(
        age_range = str_to_lower(age_range),
        age_range = str_replace( # neo ages
            age_range,
            " \\(early neonatal\\)| \\(late neonatal\\)",
            ""
        ),
        age_range = case_when( # adult ages
            age == "adult" ~ paste0(age_range, " years"),
            .default = age_range
        )
    )
df$age_range %>% unique

## Order Age Ranges

Order age ranges in sequential order.

# Get age ranges for adult
ages_adult <- df %>%
    filter(age == "adult") %>%
    pull(age_range) %>%
    unique %>%
    order_arange

# Get age ranges for child
ages_child <- df %>%
    filter(age == "child") %>%
    pull(age_range) %>%
    unique %>%
    order_arange

# Get age ranges for neo
ages_neo <- df %>%
    filter(age == "neo") %>%
    pull(age_range) %>%
    unique %>%
    order_arange

# Order age ranges as factor
df <- df %>%
    mutate(
        age_range = factor(
            age_range,
            levels = c(ages_neo, ages_child, ages_adult)
        )
    )
df$age_range %>% unique

@@

## Format Data

Format data into long form with each record consisting of one model.

Also calculates supplementary information for plots and tables.

@@

# Number of causes for each age group
ncod_adult <- 19
ncod_child <- 10
ncod_neo <- 7
ncod_all <- ncod_adult + ncod_child + ncod_neo

@@

# Pivot data into long format for calc
df_long <- df %>%
    filter( # remove low count cod
        physician_cghr10_n >= 10
    ) %>%
    pivot_longer( # long format
        ends_with("_cghr10") & !starts_with("physician_"),
        names_to = "model",
        values_to = "model_cghr10"
    ) %>%
    mutate(
        model = str_replace( # remove cghr10
            model,
            "_cghr10",
            ""
        ),
        model_name = str_replace_all(model, "_", " or ") %>% # use full model names
            str_replace(., "gpt3", gpt3_name) %>%
            str_replace(., "gpt4", gpt4_name) %>%
            str_replace(., "insilicova", isva_name) %>%
            str_replace(., "interva5", iva5_name) %>%
            factor(., levels = c(
                gpt4_name,
                gpt3_name,
                isva_name,
                iva5_name
            )),
        age_name = case_when( # use full age name
            age == "adult" ~ "Adult",
            age == "child" ~ "Child",
            age == "neo" ~ "Neonate",
            .default = NA
        ),
        cod = physician_cghr10,
        cod_name = paste0(
            cod,
            "\n(n=", physician_cghr10_n, ", ", round(physician_cghr10_perc), "%)"
        ),
        ncod = case_when( # num of cods for each age group
            age == "adult" ~ ncod_adult,
            age == "child" ~ ncod_child,
            age == "neo" ~ ncod_neo,
            .default = NA
        )
    ) %>%
    filter( # remove combine models
        !str_detect(model_name, " or ")
    )

@@

## PCCC and CSMF

# Prep data
df_plot <- df_long %>%
    group_by(model_name) %>%
    summarize(
        pccc = calc_pccc(cod, model_cghr10, N = ncod_all),
        csmf = calc_csmf_acc(cod, model_cghr10)
    ) %>%
    arrange(pccc) %>%
    mutate(
        model_name = factor(model_name, levels = model_name)
    ) %>%
    pivot_longer(
        c(pccc, csmf),
        names_to = "metric",
        values_to = "metric_value"
    ) %>%
    mutate(
        metric = str_to_upper(metric) %>%
            str_replace(., "CSMF", "CSMF Accuracy") %>%
            factor(., levels = rev(c("PCCC", "CSMF Accuracy"))),
        metric_label = paste0(metric, "=", round(metric_value, 2)) %>%
            str_replace(., " Accuracy", "")
    )

# Plot data
fig_pccc_csmf <- ggplot(
    df_plot,
    aes(
        x = metric_value,
        y = model_name,
        fill = metric
    )
) +
    geom_bar(
        stat = "identity",
        position = position_dodge(),
        color = "black",
        width = 0.7
    ) +
    geom_label(
        data = df_plot %>% filter(metric == "PCCC"),
        aes(
            label = metric_label,
            x = 0.085
        ),
        color = "black",
        fill = "white",
        size = 3,
        label.r = unit(0, "pt"),
        vjust = -0.5
    ) +
    geom_label(
        data = df_plot %>% filter(metric == "CSMF Accuracy"),
        aes(
            label = metric_label,
            x = 0.085
        ),
        color = "black",
        fill = "white",
        size = 3,
        label.r = unit(0, "pt"),
        vjust = 1.5
    ) +
    scale_fill_manual(
        values = c("black", "gray"),
        guide = guide_legend(reverse = TRUE)
    ) +
    scale_x_continuous(
        limits = c(0, 1),
        breaks = seq(0, 1, 0.1)
    ) +
    labs(
        title = NULL,
        x = NULL,
        y = NULL
    ) +
    theme_minimal() +
    theme(
        panel.border = element_rect(
            color = "black",
            fill = NA,
            linewidth = 0.75
        ),
        legend.position = c(.875, .5),
        legend.title = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(size = 10),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8)
    )

# Save plot
ggsave(
    "../manuscript/fig-pccc-csmf.pdf",
    fig_pccc_csmf,
    width = 170,
    height = 100,
    units = "mm",
    dpi = 300
)

# Display plot
fig_pccc_csmf

@@

@@

# Plot perf for pccc by age groups
fig_pccc <- plot_perf(
    df_long %>%
        mutate(
            age_label = case_when(
                age_name == "Adult"
                    ~ paste0(age_name, "\n12+ Years\n(n=", n_adult, ", ", round(perc_adult), "%)"),
                age_name == "Child"
                    ~ paste0(age_name, "\n28 Days to 11 Years\n(n=", n_child, ", ", round(perc_child), "%)"),
                age_name == "Neonate"
                    ~ paste0(age_name, "\n<28 Days\n(n=", n_neo, ", ", round(perc_neo), "%)"),
                .default = age_name
            ) %>%
                factor(., levels = unique(.) %>% sort %>% rev)
        ),
    calc_pccc,
    group = "age_label",
    x_title = "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
    text_mid_vjust = 3,
    sort_group = F,
    x_limits = c(0.2, 0.8),
    x_expand = waiver()
)

# Save plot
ggsave(
    "../manuscript/fig-pccc.pdf",
    fig_pccc,
    width = 170,
    height = 60,
    units = "mm",
    dpi = 300
)

# Display plot
fig_pccc

@@

## PCCC by Age and COD

### Adult

@@

# Plot adult perf for pccc by cod
fig_pccc_cod_adult <- plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
    x_title =  "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
    text_mid_vjust = -1,
    text_scale = 0.8
)

# Save plot
ggsave(
    "../manuscript/fig-pccc-cod-adult.pdf",
    fig_pccc_cod_adult,
    width = 170,
    height = 225,
    units = "mm",
    dpi = 300
)

# Display plot
fig_pccc_cod_adult

@@

### Child

@@

# Plot child perf for pccc by cod
fig_pccc_cod_child <- plot_perf(
    df_long %>% filter(age == "child"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Child, 28 Days to 11 Years (n=", n_child, ")"),
    x_title =  "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
    text_scale = 0.95
)

# Save plot
ggsave(
    "../manuscript/fig-pccc-cod-child.pdf",
    fig_pccc_cod_child,
    width = 170,
    height = 150,
    units = "mm",
    dpi = 300
)

# Display plot
fig_pccc_cod_child

### Neonate

@@

# Plot neo perf for pccc by cod
fig_pccc_cod_neo <- plot_perf(
    df_long %>% filter(age == "neo"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Neonatal, <28 Days (n=", n_neo, ")"),
    x_title =  "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
    text_mid_vjust = 3,
    text_end_size = 2.25,
    text_scale = 0.95
)

# Save plot
ggsave(
    "../manuscript/fig-pccc-cod-neo.pdf",
    fig_pccc_cod_neo,
    width = 170,
    height = 100,
    units = "mm",
    dpi = 300
)

# Display plot
fig_pccc_cod_neo

## PCCC by Age Range

# Format levels of age range with breaks
age_levels <- levels(df_long$age_range) %>%
    str_replace(., " ", "\n")

# Plot perf trend over age ranges
fig_pccc_age <- plot_perf_trend(
    df_long %>%
        mutate(
            age_range = str_replace(age_range, " ", "\n") %>%
                factor(., levels = age_levels)
        ),
    title = "Partial Chance Corrected Concordance (PCCC, 0=Low, 1=High)",
    text_scale = 0.9
)

# Save plot
ggsave(
    "../manuscript/fig-pccc-age.pdf",
    fig_pccc_age,
    width = 170,
    height = 100,
    units = "mm",
    dpi = 300
)

# Display plot
fig_pccc_age
